### 2016-05-09 ch03-lrm/truncation.tex
Improve list of symbols

Based on \citet{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
A \gls{SISO} \gls{LTI} system is considered.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{fig:nparam:blockH0} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
\begin{equation}\label{eq:nparam:trunc:LPM:TD}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).

@@

% \begin{assumption}
% The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
% The filtered white noise $v(t) = H_0(q)e(t)$ is the disturbing noise source at the output.
% \end{assumption}

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \latin{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

>>>>

Based on \citet{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an \gls{OE} framework. 
A \gls{SISO} \gls{LTI} system is considered.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{fig:nparam:blockH0} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
\begin{equation}\label{eq:nparam:trunc:LPM:TD}
y(t)=\true{G}(q)u_0(t)+\true{H}(q)e(t)=\true{G}(q)u_0(t)+v(t)
\end{equation}
where $\true{G}(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= \true{H}(q)e(t)$ is the noise source at the output, $\true{H}(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).

@@

% \begin{assumption}
% The measured output signal is $y(t) = y_0(t) + v(t)$ with the exact input signal $u_0(t)$ known. 
% The filtered white noise $v(t) = \true{H}(q)e(t)$ is the disturbing noise source at the output.
% \end{assumption}

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \latin{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=\true{G}(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = \true{H}(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

### 2016-05-09 config/glossaries.inc.tex
Some stuff, here and there
Some cleanup, more references input design
Improve list of symbols

\newsymbolglos{A-SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{A-SetZ}{\IntegerNumbers}{Set of integer numbers}
\newsymbolglos{A-SetQ}{\RationalNumbers}{Set of the rational numbers}
\newsymbolglos{A-SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{A-SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{A-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
\newsymbolglos{A-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
\newsymbolglos{A-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
\newsymbolglos{A-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}

\newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
% \newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}

\newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
\newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}

\newsymbolglos{E-approx}{\approx}{is approximately equal to \ldots}
\newsymbolglos{E-bydef}{\isdef}{is defined as \ldots}
\newsymbolglos{E-propto}{\propto}{is proportional to \ldots}
\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
\newsymbolglos{E-ll}{\ll}{is much smaller than \ldots}
\newsymbolglos{E-gg}{\gg}{is much greater than \ldots}

\newsymbolglos{lcm}{\lcm}{Least common multiple}

\newsymbolglos{matrix-eye-square}{\Identity{n}}{$n \times n$ identity matrix}
\newsymbolglos{matrix-eye}{\Identity{n \times m}}{$n \times m$ identity matrix}
\newsymbolglos{matrix-zero}{\Zero{n\times m}}{ $n \times m$ matrix containing only zeros}

\newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
\newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}
\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}

\newsymbolglos{operator-bias}{\bias{\placeholder}}{Bias of \placeholder}
\newsymbolglos{operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{operator-exp}{\E{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-ln}{\ln}{Natural logarithm}
\newsymbolglos{operator-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}
\newsymbolglos{operator-matrix-conv}{\conv}{Convolution}
\newsymbolglos{operator-matrix-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}
\newsymbolglos{operator-matrix-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{operator-matrix-kron}{\kron}{Kronecker product of matrices (\code{kron})}
\newsymbolglos{operator-matrix-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-matrix-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
\newsymbolglos{operator-var}{\var{\placeholder}}{Variance of \placeholder}

\newsymbolglos{sys-damping}{\damping}{Relative damping of a pole or system}
\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a pole or system}
\newsymbolglos{sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}

\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}

%% ACRONYMS
\setulcolor{gray}
%\newcommand{\abbrev}[1]{\ul{#1}}
\newcommand{\abbrev}[1]{#1}

\newacronym{ADC}{ADC}{analog-to-digital converter}
\newacronym{AICc}{AICc}{Akaike's information criterion corrected for small sample sizes}
\newacronym{AIC}{AIC}{Akaike's information criterion}
\newacronym{AVIS}{AVIS}{active vibration isolation system}

\newacronym{BLA}{BLA}{\abbrev{b}est \abbrev{l}inear \abbrev{a}pproximation}
\newacronym{BK}{B\&K}{\bruelkjaer}
\newacronym{BNC}{BNC}{Bayonet Neill-Concelman (connector)}
\newacronym{BTLS}{BTLS}{\abbrev{b}ootstrapped \abbrev{t}otal \abbrev{l}east \abbrev{s}quares}

\newacronym{CDF}{CDF}{cumulative distribution function}
\newacronym{CPU}{CPU}{central processing unit}
\newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
\newacronym{CZT}{CZT}{chirp $Z$-transform}

\newacronym{DAC}{DAC}{digital-to-analog converter}
\newacronym{DAQ}{DAQ}{data acquisition}
\newacronym{DC}{DC}{direct current (also: mean value)}
\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{PDF}{PDF}{probability distribution function}
\newacronym{PI}{PI}{proportional-integral}
\newacronym{PRESS}{PRESS}{prediction residual error sum of squares}
\newacronym{PSD}{PSD}{power spectral density}

\newacronym{RAM}{RAM}{random-access memory}
\newacronym{RARX}{RARX}{\abbrev{r}egularized \abbrev{a}uto-\abbrev{r}egressive e\abbrev{x}ogenous}
\newacronym{RCF}{RCF}{right co-prime factorization}
\newacronym{RFIR}{RFIR}{\abbrev{r}egularized \abbrev{f}inite \abbrev{i}mpulse \abbrev{r}esponse}
\newacronym{RMS}{RMS}{\abbrev{r}oot-\abbrev{m}ean-\abbrev{s}quare}
\newacronym{RMSE}{RMSE}{\abbrev{r}oot \abbrev{m}ean \abbrev{s}quared \abbrev{e}rror}

@@

\newacronym{VME}{VME}{Versa Module Eurocard (\glsentrytext{IEEE} 1014)}
\newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
\newacronym{VXI}{VXI}{\abbrev{V}ME e\abbrev{x}tensions for \abbrev{i}nstrumentation}

>>>>

\newsymbolglos{A1-SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{A2-SetZ}{\IntegerNumbers}{Set of integer numbers}
\newsymbolglos{A3-SetQ}{\RationalNumbers}{Set of the rational numbers}
\newsymbolglos{A4-SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{A5-SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{A6-SetNnozero}{\NaturalNumbersWithoutZero}{Set of the natural numbers without the number $0$}
\newsymbolglos{A7-SetRnozero}{\RealNumbersWithoutZero}{Set of the positive real numbers without the number $0$, i.e. $\RealNumbers \without \set{0}$}
\newsymbolglos{A8-SetRpos}{\PositiveRealNumbers}{Set of the positive real numbers}
\newsymbolglos{A9-SetRneg}{\NegativeRealNumbers}{Set of negative real numbers}

\newsymbolglos{B-imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{B-w}{\omega}{Frequency ($\unit{Hz}$) or angular frequency ($\unit{rad/s}$)}
% \newsymbolglos{B-epsilon}{\eps}{The numerical precision of a floating point number (\code{eps}), e.g. $\eps \approx 2.2 \cdot 10^{-16}$ for \code{double} precision}
\newsymbolglos{B-sys-damping}{\damping}{Relative damping of a pole or system}
\newsymbolglos{B-sys-resonance}{\wn}{Natural (resonance) frequency of a pole or system}
\newsymbolglos{B-sys-timeconst}{\timeconst}{Time constant of a pole or system ($\timeconst \isdef (\damping \wn)^{-1}$)}
\newsymbolglos{B-sys-shiftoperator}{q}{Forward shift operator ($qu(t) = u(t+1)$)}
\newsymbolglos{B-sys-laplaceoperator}{s}{Laplace variable}

\newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
\newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}
\newsymbolglos{count-window}{\nWind}{Bandwidth of local window}
\newsymbolglos{count-order}{\order{A},\order{B},\order{C}}{Order of local models $\LocalModel{A}, \LocalModel{B},\LocalModel{C}$}

\newsymbolglos{E-approx}{\approx}{is approximately equal to \ldots}
\newsymbolglos{E-def}{\isdef}{is defined as \ldots}
\newsymbolglos{E-distributed}{\distributedAs}{is distributed as \ldots}
\newsymbolglos{E-equiv}{\equiv}{is equivalent with \ldots}
\newsymbolglos{E-propto}{\propto}{is proportional to \ldots}
\newsymbolglos{E-ll}{\ll}{is much smaller than \ldots}
\newsymbolglos{E-gg}{\gg}{is much greater than \ldots}

\newsymbolglos{F-lcm}{\lcm}{Least common multiple}
\newsymbolglos{F-ln}{\ln}{Natural logarithm}
\newsymbolglos{F-log}{\log_{B}}{Logarithm in base $B$ (when $B$ is omitted, $B=10$ is implied)}

\newsymbolglos{G-statOperator-bias}{\bias{\placeholder}}{Bias of \placeholder}
\newsymbolglos{G-statOperator-var}{\var{\placeholder}}{Variance of \placeholder}
\newsymbolglos{G-statOperator-exp}{\E{\placeholder}}{Expected value of \placeholder}

\newsymbolglos{M-matrix-eye-square}{\Identity{n}}{$n \times n$ identity matrix}
\newsymbolglos{M-matrix-eye}{\Identity{n \times m}}{$n \times m$ identity matrix}
\newsymbolglos{M-matrix-zero}{\Zero{n\times m}}{ $n \times m$ matrix containing only zeros}

\newsymbolglos{O-matrix-operator-conj}{\conj \placeholder}{Complex conjugate of \placeholder}
\newsymbolglos{O-matrix-operator-ht}{\placeholder^{\HT}}{Hermitian (complex conjugated) transpose of the matrix \placeholder}
\newsymbolglos{O-matrix-operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{O-matrix-operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{O-operator-cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{O-operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{O-operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{O-operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer, as in \glsentrytext{IEEE} 754-2008 (\code{round})}
\newsymbolglos{O-operator-bigO}{\bigO{\placeholder}}{Bachmann-Landau ``big oh'' notation for the order of a function}

\newsymbolglos{P-product-kron}{\kron}{Kronecker product of matrices (\code{kron})}
\newsymbolglos{P-product-conv}{\conv}{Convolution}
\newsymbolglos{P-product-hadamard}{\hadamard}{Hadamard (element-wise) product of matrices (\code{.*})}

\newsymbolglos{N-norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
\newsymbolglos{N-norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
\newsymbolglos{N-norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}

%% ACRONYMS
\newacronym{ADC}{ADC}{analog-to-digital converter}
\newacronym{AICc}{AICc}{Akaike's information criterion corrected for small sample sizes}
\newacronym{AIC}{AIC}{Akaike's information criterion}
\newacronym{AVIS}{AVIS}{active vibration isolation system}

\newacronym{BLA}{BLA}{best linear approximation}
\newacronym{BK}{B\&K}{\bruelkjaer}
\newacronym{BNC}{BNC}{Bayonet Neill-Concelman (connector)}
\newacronym{BTLS}{BTLS}{bootstrapped total least squares}

\newacronym{CDF}{CDF}{cumulative density function}
\newacronym{CPU}{CPU}{central processing unit}
\newacronym{CRLB}{CRLB}{Cramér-Rao lower bound}
\newacronym{CZT}{CZT}{chirp $Z$-transform}

\newacronym{DAC}{DAC}{digital-to-analog converter}
\newacronym{DAQ}{DAQ}{data acquisition}
\newacronym{DC}{DC}{static}
\newacronym{DCkernel}{DC kernel}{diagonal correlated kernel}
\newacronym{DFT}{DFT}{discrete Fourier transform}
\newacronym{DSA}{DSA}{dynamic signal analyzer}
\newacronym{DTFT}{DFT}{discrete-time Fourier transform}
\newacronym{DUT}{DUT}{device under test}

@@

\newacronym{PDF}{PDF}{probability density function}
\newacronym{PI}{PI}{proportional-integral}
\newacronym{PRESS}{PRESS}{prediction residual error sum of squares}
\newacronym{PSD}{PSD}{power spectral density}

\newacronym{RAM}{RAM}{random-access memory}
\newacronym{RARX}{RARX}{regularized auto-regressive exogenous}
\newacronym{RCF}{RCF}{right co-prime factorization}
\newacronym{RFIR}{RFIR}{regularized finite impulse response}
\newacronym{RMS}{RMS}{root-mean-square}
\newacronym{RMSE}{RMSE}{root mean squared error}

@@

\newacronym{VME}{VME}{Versa Module Eurocard (\glsentrytext{IEEE} 1014)}
\newacronym{VUB}{VUB}{Vrije Universiteit Brussel}
\newacronym{VXI}{VXI}{VME extensions for instrumentation}
